FIXME

### 2013-10-02 writeups/proposal/proposal.tex
foo
Former-commit-id: 496906991ccc1838e6d8ce6e58f21a590d6e5c80 [formerly 4055675559ae36636d274c3b8730857928e72e31]
Former-commit-id: 5deef66a6f58b7738b3c495df534f741a44cc3b6
foo
Former-commit-id: 099d5e79dc25877fdd408c2362508b0c4d91658d [formerly 9b750697e007311bee146ed5a16ba135990ae585]
Former-commit-id: 51c0a167072d907de440011535b6cb38dfb57840

\usepackage{csquotes}
\usepackage[style=apa,sortcites=true,sorting=nyt,backend=biber,doi=false,uniquename=false]{biblatex}
\DeclareLanguageMapping{american}{american-apa}
\addbibresource{bibliography.bib}

@@

@@

% FIXME: Fix cite for Bauer2012
One traditional technique is to provide the user with a powerful search engine so that they can actively look for content that interests them.
However, users are not forming the same search queries that work so effectively on search engines like Google.
A growing number of users on social media sites are searching for information that is happening now, in real time \parencites{Bauer2012,Jansen2011}.
In other words, users on social-media sites want the fresh \emph{stream} of information about a particular topic.
This can certainly be seen in the main user-interface views that these social media site provide:
Twitter's homepage showing your followers' tweets, Facebook's homepage showing your friends' posts, StackOverflow's daily digest of posts for particular tags.

@@

% FIXME: Use vector-graphics for this figure 
\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{stackoverflowPostExample1-crop.pdf}}}
  \caption{Example post on stackoverflow.com}
  \label{figSOExample}
\end{figure}

@@

% FIXME: Fix cite for Bennett2007
The Netflix Prize \parencite{Bennett2007} is an example of a recommendation system where prior user behavior and current context was used to present the most relevant information to the user.
Netflix is an online-subscription service where users can stream their favorite television episodes and movies.
Each user of the site is only interested in a small portion of the entire library of content that Netflix provides.
In order to provide a high-quality user experience on the site, Netflix created a content-recommendation service.
This tool recommends to the user movies and television episodes that most likely match their specific interests.

@@

% FIXME: Add figure for LaTeX tag suggestion example

A tag suggestion tool has been deployed for the \url{http://tex.stackexchange.org} site \parencite{LatexTags2013}.
Both the \LaTeX site and StackOverflow are part of the broader StackExchange network of question and answer sites, and they provide the same user interface and workflow when asking questions.
Once a user has created a question on the Latex site, the site provides subdued text of suggested tags in the text field where the user fills in the tags to associate with the question.
The post author is not forced to use the suggested tags, and is free to choose tags from them or tags not represented in the suggested set.

The Latex site is not nearly as popular as StackOverflow currently.
The site has roughly \num{50000} questions compared to \num{5000000} questions on StackOverflow.
It may be the case that the StackExchange company decided to try out a tag recommendation system on one of their smaller sites first, before deploying this type of system on their most popular StackOverflow site.
Or it is possible that their current tag recommendation system is not efficient enough to work with the demand of the StackOverflow site.
Nonetheless, it is encouraging that StackExchange finds tag recommendation models beneficial enough to the user to start adding them to their question and answer sites.

>>>>

\usepackage{csquotes}
\usepackage[style=apa,sortcites=true,sorting=nyt,backend=biber,doi=false,uniquename=false]{biblatex}
\DeclareLanguageMapping{american}{american-apa}

\addbibresource{bibliography.bib}

@@

% Don't let biblatex change any of the casing in the bibliography file
\DeclareRobustCommand{\MakeSentenceCase*}[1]{{#1}}

@@

One traditional technique is to provide the user with a powerful search engine so that they can actively look for content that interests them.
However, users are not forming the same search queries that work so effectively on search engines like Google.
A growing number of users on social media sites are searching for information that is happening now, in real time \parencite{Jansen2011}.
In other words, users on social-media sites want the fresh \emph{stream} of information about a particular topic.
This can certainly be seen in the main user-interface views that these social media site provide:
Twitter's homepage showing your followers' tweets, Facebook's homepage showing your friends' posts, StackOverflow's daily digest of posts for particular tags.

@@

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{stackoverflowPostExample1-crop.pdf}}}
  \caption{Example post on stackoverflow.com}
  \label{figSOExample}
\end{figure}

@@

The Netflix Prize \parencite{Bennett2007} is an example of a recommendation system where prior user behavior and current context was used to present the most relevant information to the user.
Netflix is an online-subscription service where users can stream their favorite television episodes and movies.
Each user of the site is only interested in a small portion of the entire library of content that Netflix provides.
In order to provide a high-quality user experience on the site, Netflix created a content-recommendation service.
This tool recommends to the user movies and television episodes that most likely match their specific interests.

@@

A tag suggestion tool has been deployed for the \url{http://tex.stackexchange.org} \parencite{LatexTags2013} and \url{http://superuser.com} \parencite{SuperUserTags2013} StackExchange sites.
\LaTeX, SuperUser, and StackOverflow are all part of the broader StackExchange network of question and answer sites, and they provide the same user interface and workflow when asking questions.
For the two sites where a tag suggestion tool has been deployed, once a user has created a question, suggested tags appear just below the text field where the user types the tags to associate with the question.
The post author is not forced to use the suggested tags, and is free to choose tags from them or tags not represented in the suggested set.
An example of the interface for a created post on the SuperUser site is included in Figure \ref{figSuperUserSuggestion}.

\begin{figure}[!htbp]
  \scalebox{.9}{\resizebox{\linewidth}{!}{\includegraphics{superUserTagSuggestion.pdf}}}
  \caption{Example of tag suggestions when creating a post on the SuperUser site}
  \label{figSuperUserSuggestion}
\end{figure}

The Latex and SuperUser sites are not nearly as popular as StackOverflow currently.
The sites have roughly \num{50000} and \num{189000} questions respectively compared to \num{5000000} questions on StackOverflow.
It may be the case that StackExchange decided to try out a tag recommendation system on a few of their smaller sites first, before deploying this type of system on their most popular StackOverflow site.
Or it is possible that their current tag recommendation system is not efficient enough to work with the demand of the StackOverflow site.
Nonetheless, it is encouraging that StackExchange finds tag recommendation models beneficial enough to the user to start adding them to their question and answer sites.
